%!TEX root = ../main.tex
\section{A concrete realization: the clamped--free corner under compression}
\label{sec:concrete}

The preceding analysis is deliberately abstract: it isolates the structural properties of the energy
(Assumptions~\ref{ass:reg}--\ref{ass:mild}) and of the loading (the hypotheses of \S\ref{sec:iba}) that the argument
actually uses, without committing to a domain. We now fix a concrete material and a concrete family of geometries and
ask how much of that hypothesis list can be \emph{discharged} rather than assumed. The material is the compressible
neo-Hookean energy \eqref{eq:neohooke} with the barrier penalty $f_{\log}$. The geometry is a body whose boundary
carries a clamped (Dirichlet) face meeting a traction-free (Neumann) face at a right angle, under a compressive load.

The abstract development of \S\ref{sec:asymptotics}--\S\ref{sec:iba} is already dimension-independent: it analyses the
transverse problem at the codimension-two Dirichlet--Neumann edge $\Sigma$ in $\mathbb{R}^d$. Here we instantiate it on
concrete bodies and ask how much of that hypothesis list can be \emph{discharged} rather than assumed.

\subsection{Geometry and the singular set}
\label{sub:geom}

We consider two model bodies in $\Omega\subset\mathbb{R}^d$.

\begin{itemize}
    \item \textbf{(H) Half-ball.} $\Omega = \{\,\bm{x}\in\mathbb{R}^d : |\bm{x}|<1,\ x_d>0\,\}$. The flat base
          $\Gamma_D=\{x_d=0\}\cap\partial\Omega$ is clamped; the spherical cap $\Gamma_N=\{|\bm{x}|=1\}\cap\partial\Omega$ is
          traction-free.
    \item \textbf{(C) Box.} $\Omega=(-1,1)^{d-1}\times(0,1)$. The base $\Gamma_D=\{x_d=0\}$ is clamped; the remaining faces
          are traction-free.
\end{itemize}

In both cases the load is a monotone compression transmitted through $\Gamma_N$ (a pressure or an inward normal
displacement on the cap, respectively the lateral/top faces), scaled by the pseudo-time $t\in[0,1]$ of \S\ref{sec:iba}.

The \emph{singular set} $\Sigma\subset\partial\Omega$ is the locus where $\overline{\Gamma_D}$ meets
$\overline{\Gamma_N}$:
\begin{itemize}
    \item for (H), $\Sigma=\{|\bm{x}|=1,\ x_d=0\}\cong S^{d-2}$, a \emph{smooth} codimension-two submanifold; the cap is
          tangent to the vertical at the equator, so it meets the horizontal base at a right angle;
    \item for (C), $\Sigma$ is the union of the bottom edges $\{x_d=0,\ x_i=\pm1\}$, again right-angle Dirichlet--Neumann
          edges, \emph{together with} the bottom vertices, where $d$ faces meet.
\end{itemize}

Fix $\bm{x}_0\in\Sigma$ away from any vertex and split $\mathbb{R}^d=T_{\bm{x}_0}\Sigma\oplus\Pi$, with $\Pi$ the
two-plane normal to $\Sigma$. In the slice $\Pi$ the boundary reduces to a Dirichlet ray and a Neumann ray meeting at
$90^\circ$: \emph{exactly} the planar junction of \S\ref{sub:scenarioA}. We write $B_\rho$ for a tubular neighbourhood
of $\Sigma$ of radius $\rho$ and use $(r,\theta)$ for polar coordinates in $\Pi$ as before.

\begin{remark}[Why the half-ball is the clean model]
    \label{rem:cleanmodel}
    For (H) the singular set $\Sigma$ is a smooth closed manifold with no vertices, so the singularity is a \emph{pure
        edge} everywhere on $\Sigma$ and the transverse problem is the planar right-angle junction at every point. For (C)
    the edge interiors behave identically, but the bottom vertices carry an additional, generally stronger,
    polyhedral-vertex singularity \cite{MazyaRossmann2010} that is outside the scope of the edge analysis; one either
    rounds the vertices or restricts $B_\rho$ to the edge interior. We therefore state the dimension-independent results
    for (H) and note that they hold verbatim on the edge interiors of (C).
\end{remark}

\subsection{Tier 1: the material assumptions are already discharged}
\label{sub:tier1}

For the neo-Hookean energy \eqref{eq:neohooke} with $f_{\log}$, the standing assumptions of
\S\ref{sec:asymptotics} hold with explicit constants and require no information about the domain:
Assumption~\ref{ass:reg} (regularity, objectivity, and the collapse barrier $f_{\log}(J)\to\infty$),
Assumption~\ref{ass:growth} (the inverse-channel bound, with $\Theta=\Theta_{\log}$ of \eqref{eq:Thetalog}),
Assumption~\ref{ass:ellip} and the sharper Lemma~\ref{lem:SEcompress} (strong ellipticity with constant $\ge\mu_e$
throughout compression), and Assumption~\ref{ass:mild} (logarithmic growth, $p=1$) are all established in
Lemma~\ref{lem:nh}, Remark~\ref{rem:SEcaveat} and \S\ref{sub:growth}. None of these proofs uses $d=2$: the tangent
formula \eqref{eq:Lnh}, the rank-one identity \eqref{eq:LHnh}, and the growth functions \eqref{eq:Thetalog} are
algebraic identities in $\mathrm{GL}^+(d)$. Thus the entire material side of the hypothesis list is closed for the
concrete model, in every dimension. What remains are the hypotheses on the \emph{solution and loading}, which is where
the geometry enters.

\subsection{The edge exponent and the scenario it selects}
\label{sub:edgeexp}

By the edge-singularity calculus \cite{KMR2001,MazyaRossmann2010}, the leading singular exponents of the linearised
elasticity operator along the smooth edge $\Sigma$ coincide with those of the transverse two-dimensional pencil in
$\Pi$, modulated smoothly along $\Sigma$. That transverse pencil is the planar right-angle Dirichlet--Neumann corner of
\eqref{eq:kondratiev}; its leading exponent $\alpha\in(0,1)$ is the smallest root of the corresponding
clamped--free Williams secular equation and depends only on the Poisson ratio. Consequently the kinematic blow-up
\eqref{eq:Fblowup}, $\bm{F}=\bm{I}+\mathcal{O}(r^{\alpha-1})$, holds with a \emph{computable} exponent, and by
Theorem~\ref{thm:A} the nonlinear tangent inherits exactly this $\alpha$ in the benign regime --- on the annulus
outside the dilation core of Lemma~\ref{lem:Aellip}, the core being absent for mild loading or a globally
convex-volumetric barrier.

Which scenario of \S\ref{sec:asymptotics} is realized is governed by the sign of the dominant eigenvalue of
$\Grad\bm{u}$ at the edge, equivalently by the sign of the stress-intensity factor $K$ in \eqref{eq:kondratiev}. This is
a global quantity, set by the far field, and is not determined by the local pencil alone. The compressive load we
impose selects $K<0$: the material is pushed into the corner, the dominant eigenvalue of $\Grad\bm{u}$ is negative,
and Scenario~B (\S\ref{sub:scenarioB}) is the relevant branch. The quantitative form of ``compressive enough'' is the
hypothesis (SC) below; it simultaneously selects Scenario~B and drives the structural instability of
\S\ref{sub:concrete-tc}. The complementary tensile load ($K>0$) selects Scenario~A, where (NC) holds and
Theorem~\ref{thm:A} applies; for the present geometry under compression that case does not arise near the edge.

\subsection{Existence of the critical load via a localized surface instability}
\label{sub:concrete-tc}

The one genuinely non-elementary ingredient of \S\ref{sec:iba} was hypothesis (ii) of Lemma~\ref{lem:tc}: the
existence of a structurally destabilising field, $Q_{t_*}(\bm{v}_*)<0$, which we there declined to establish and
flagged as the corner counterpart of the Biot/creasing instability. For the concrete clamped--free geometry we now
\emph{prove} it, by reduction to the surface instability of the compressed half-space.

The free face $\Gamma_N$ under compression is, locally, a traction-free surface compressed parallel to itself --- the
exact configuration of Biot's classical analysis \cite{Biot1963}. A homogeneously compressed neo-Hookean half-space
loses stability to a surface mode once the surface-parallel stretch falls below a threshold
$\lambda_\star\in(0,1)$ (for the incompressible model $\lambda_\star\approx0.544$; for the compressible energy
\eqref{eq:neohooke} the threshold is the corresponding root of the surface secular equation, still in $(0,1)$
\cite{Hong2009}). We package the loading requirement as a single hypothesis.

\begin{assumption}[Surface compression reaches threshold, (SC)]
    \label{ass:sc}
    There exist $t_*\in(0,1]$ and an interior point $P\in\Gamma_N\cap B_\rho$, at positive distance from both $\Sigma$
    and $\overline{\Gamma_D}$, such that the fundamental state compresses the free face below the half-space threshold
    there: the surface-parallel principal stretch of $\bm{F}_0(t_*)$ at $P$ satisfies
    $\lambda_\parallel\big(\bm{F}_0(t_*);P\big)<\lambda_\star$.
\end{assumption}

\noindent (SC) is an input on the \emph{loading}, in the same spirit as the monotonicity condition (M) of
Lemma~\ref{lem:transversal}: it says only that the prescribed compression is strong enough that the free surface dips
below its own buckling threshold somewhere near the edge. Since $t$ merely normalises the load amplitude, (SC) can
always be met by loading hard enough, provided the material does not fail elsewhere first.

\begin{lemma}[Localized surface instability $\Rightarrow$ structural instability]
    \label{lem:biot}
    Under Assumption~\ref{ass:sc}, hypothesis (ii) of Lemma~\ref{lem:tc} holds: there is $\bm{v}_*\in V$, supported in
    $B_\rho$ and vanishing on $\Gamma_D$, with
    \begin{equation}
        \label{eq:Qneg}
        Q_{t_*}(\bm{v}_*) = \int_{B_\rho}\Grad\bm{v}_* : \mathbb{L}\big(\bm{F}_0(t_*)\big) : \Grad\bm{v}_*\,dV < 0 .
    \end{equation}
    Consequently, with $\mu_1(0)>0$ from Lemma~\ref{lem:tc}(i), there is a first critical load $t_c\in(0,t_*]$ with
    $\mu_1(t_c)=0$.
\end{lemma}

\begin{proof}
    Work in coordinates centred at $P$: let $n\ge0$ be the depth into the body along the inward normal to $\Gamma_N$ and
    $\bm{s}\in\mathbb{R}^{d-1}$ the surface-tangent coordinates, so that near $P$ the body is the half-space $\{n>0\}$ and
    $\bm{F}_0(t_*)$ is $C^1$ with value $\bm{F}_P:=\bm{F}_0(t_*;P)$ whose surface-parallel stretch is
    $\lambda_\parallel<\lambda_\star$.

    \emph{Step 1: the homogeneous unstable mode.} Freeze the coefficients at $\bm{F}_P$ and consider the constant-tensor
    form $Q_0(\bm{v})=\int_{\{n>0\}}\Grad\bm{v}:\mathbb{L}(\bm{F}_P):\Grad\bm{v}\,dV$ on the half-space, with $\bm{v}$
    traction-free at $n=0$. Because $\lambda_\parallel<\lambda_\star$, the half-space is past its surface-instability
    threshold \cite{Biot1963,Hong2009}: for each surface wavevector $\bm{k}\in\mathbb{R}^{d-1}$, $k:=|\bm{k}|$, there is a
    surface mode
    \begin{equation}
        \label{eq:biotmode}
        \bm{v}_{\bm{k}}(\bm{s},n) = \mathrm{Re}\,\big[\,\hat{\bm{v}}(kn)\,e^{\mathrm{i}\bm{k}\cdot\bm{s}}\,\big],
        \qquad |\hat{\bm{v}}(\zeta)|\le C e^{-\beta\zeta}\ (\beta>0),
    \end{equation}
    decaying exponentially into the body on the depth scale $1/k$. Since $\mathbb{L}(\bm{F}_P)$ is constant, the rescaling
    $(\bm{s},n)\mapsto k^{-1}(\bm{s},n)$ shows that over a surface window $W$ of area $|W|$,
    \begin{equation}
        \label{eq:biotscale}
        \int_{\{n>0\}} \mathbf{1}_W\,\Grad\bm{v}_{\bm{k}}:\mathbb{L}(\bm{F}_P):\Grad\bm{v}_{\bm{k}}\,dV
        = q(\lambda_\parallel)\,k\,|W|\,(1+o(1)), \qquad q(\lambda_\parallel)<0,
    \end{equation}
    where $q$ is the Biot secular form, strictly negative past threshold. Likewise
    $\int_{\{n>0\}}\mathbf{1}_W\,|\Grad\bm{v}_{\bm{k}}|^2 \sim k\,|W|$ and
    $\int_{\{n>0\}}\mathbf{1}_W\,|\bm{v}_{\bm{k}}|^2 \sim k^{-1}|W|$, the latter two by the same scaling.

    \emph{Step 2: cut-off.} Let $\chi$ be smooth, $\chi\equiv1$ on $B(P,\delta/2)$, $\mathrm{supp}\,\chi\subset
        B(P,\delta)$, $|\Grad\chi|\le C/\delta$, with $\delta$ small enough that $B(P,\delta)\cap\overline\Omega$ avoids
    both $\Sigma$ and $\overline{\Gamma_D}$ and lies in $B_\rho$ (possible since $P$ is at positive distance from both).
    Set $\bm{v}_*:=\chi\,\bm{v}_{\bm{k}}$. Then $\bm{v}_*\in V$ and vanishes on $\Gamma_D$ (its support avoids
    $\overline{\Gamma_D}$); it is unconstrained on the free face, as required.

    \emph{Step 3: error control.} Write $\Grad\bm{v}_*=\chi\Grad\bm{v}_{\bm{k}}+(\Grad\chi)\otimes\bm{v}_{\bm{k}}$ and
    expand \eqref{eq:Qneg}. The effective window is $W\sim B(P,\delta)\cap\Gamma_N$, of area $|W|\sim\delta^{d-1}$, and the
    decay confines the mass to depth $1/k$. Three errors arise.
    \begin{enumerate}
        \item[(a)] \emph{Coefficient variation:} replacing $\mathbb{L}(\bm{F}_0(\bm{x}))$ by $\mathbb{L}(\bm{F}_P)$ costs
              $\le \sup_{B(P,\delta)}\|\mathbb{L}(\bm{F}_0)-\mathbb{L}(\bm{F}_P)\|\int\chi^2|\Grad\bm{v}_{\bm{k}}|^2
                  \le C\delta\cdot k\delta^{d-1}=Ck\delta^{d}$ (by $C^1$ regularity of $\bm{F}_0$ at $P$).
        \item[(b)] \emph{Gradient commutator:} the cross term and $|\Grad\chi|^2|\bm{v}_{\bm{k}}|^2$ term are bounded by
              $C\big(\delta^{-1}\!\!\int_W |\bm{v}_{\bm{k}}||\Grad\bm{v}_{\bm{k}}| + \delta^{-2}\!\!\int_W|\bm{v}_{\bm{k}}|^2\big)
                  \le C\big(\delta^{d-2} + \delta^{d-3}k^{-1}\big)$.
        \item[(c)] \emph{Window vs.\ cut-off:} replacing $\mathbf{1}_W$ by $\chi^2$ in \eqref{eq:biotscale} changes the
              leading constant by $1+o(1)$ only.
    \end{enumerate}
    The leading term is $q(\lambda_\parallel)\,k\,\delta^{d-1}<0$. The errors (a)--(b), relative to it, are
    $\mathcal{O}(\delta)$, $\mathcal{O}((k\delta)^{-1})$ and $\mathcal{O}((k\delta)^{-2})$. Choosing $\delta=k^{-1/2}$
    sends $\delta\to0$ and $k\delta=k^{1/2}\to\infty$, so all relative errors vanish as $k\to\infty$. Hence for $k$ large
    enough,
    \[
        Q_{t_*}(\bm{v}_*) = q(\lambda_\parallel)\,k\,\delta^{d-1}\,(1+o(1)) < 0,
    \]
    which is \eqref{eq:Qneg}. The final statement is Lemma~\ref{lem:tc} with hypothesis (ii) now supplied. \qed
\end{proof}

\begin{remark}[What this closes]
    Lemma~\ref{lem:biot} converts the existence of the critical load $t_c$ --- previously conditional on the unproved
    hypothesis (ii) --- into a \emph{theorem} for the concrete clamped--free geometry, contingent only on the loading
    hypothesis (SC). The mechanism is made explicit: the corner instability \emph{is} the half-space surface (creasing)
    instability, localised to the free face near the edge by the cut-off \eqref{eq:biotmode}--\eqref{eq:biotscale}. This
    is the precise sense in which the corner bifurcation is ``the corner analogue of creasing.''
\end{remark}

\begin{remark}[On the threshold $\lambda_\star$: compressible vs.\ incompressible]
    \label{rem:threshold}
    The proof uses only the \emph{existence} of a surface-instability threshold $\lambda_\star\in(0,1)$, not its value.
    The familiar number $\lambda_\star\approx0.544$ is Biot's result for the \emph{incompressible} neo-Hookean half-space
    \cite{Biot1963}; the present material \eqref{eq:neohooke} is compressible, and its threshold is the corresponding root
    of the compressible surface secular equation, which depends on the ratio $\lambda_e/\mu_e$ (equivalently the Poisson
    ratio) and tends to $0.544$ in the incompressible limit $\lambda_e/\mu_e\to\infty$ \cite{Hong2009}. This is the same
    instability with a material-dependent threshold, not a discrepancy: Lemma~\ref{lem:biot} \emph{reduces} the corner
    instability to the half-space one and thereby agrees with the creasing literature rather than competing with it.
    Accordingly we keep $\lambda_\star$ symbolic throughout.
\end{remark}

\subsection{Symmetry: simplicity of the mode and the vanishing quadratic}
\label{sub:symmetry}

Both model bodies of \S\ref{sub:geom} possess reflection symmetries that the fundamental compressive state inherits:
(H) is invariant under every orthogonal map fixing the $x_d$-axis, and (C) under each coordinate reflection
$x_i\mapsto-x_i$ ($i<d$). Let $R$ be such a reflection and $\mathcal{R}$ its action on displacement fields. Because
$\bm{F}_0(t)$ and hence $\mathbb{L}(\bm{F}_0(t))$ are $R$-invariant, the second-variation operator $\mathcal{L}(t)$
commutes with $\mathcal{R}$, so its eigenspaces split into the symmetric ($\mathcal{R}=+1$) and antisymmetric
($\mathcal{R}=-1$) sectors. This yields, for the concrete geometry, two of the ingredients that \S\ref{sec:iba} had to
posit:

\begin{itemize}
    \item \emph{Simplicity (part of Assumption~\ref{ass:bif}).} The lowest eigenvalue within a fixed symmetry sector is
          generically simple, and the critical mode $\bm{\phi}$ is the ground state of one sector; the genericity is the
          standard one for self-adjoint operators commuting with a finite symmetry group. Thus simplicity need not be
          assumed separately --- only the spectral \emph{attainment} (the borderline-elliptic point of
          Remark~\ref{rem:framework}) remains genuinely open.
    \item \emph{Vanishing quadratic coefficient (part of Assumption~\ref{ass:subcrit}).} The reduced potential of
          Proposition~\ref{prop:LS} inherits the $\mathcal{R}$-symmetry of the perfect state. If $\bm{\phi}$ lies in the
          antisymmetric sector then $w\mapsto-w$ is a symmetry of the reduced equation, forcing the quadratic coefficient
          to vanish exactly, as Assumption~\ref{ass:subcrit} stipulated ``by the reflection symmetry about the corner
          bisector.'' Here that bisector symmetry is realized concretely by $R$.
\end{itemize}

What symmetry does \emph{not} give is the sign of the cubic, $b<0$; that is the irreducible core addressed below.

\subsection{Kinematic relief}
\label{sub:reliefd}

The kinematic relief is already dimension-independent, and --- in contrast to the original formulation --- it no longer
rests on an assumed rotation condition. Earlier drafts \emph{posited} that the critical mode be exactly
volume-preserving at first order, $\operatorname{cof}\bm{F}_0:\Grad\bm{\phi}=0$. That hypothesis is now \emph{discharged}:
Lemma~\ref{lem:rot} bounds the first-order volume change by the barrier alone,
$D_1=\operatorname{cof}\bm{F}_0:\Grad\bm{\phi}=\mathcal{O}(J_0/\sqrt{|\log J_0|})$ --- small with $J_0$, but not assumed
zero --- and Lemma~\ref{lem:relief} then proves the unconditional lower bound
\begin{equation}
    \label{eq:reliefd}
    J=J_0+w\,D_1+w^2 d_\phi+\mathcal{O}(w^3) \ \ge\ \tfrac12 J_0+\tfrac12 w^2 d_\phi
    \qquad\text{in } \mathbb{R}^d,
\end{equation}
with $d_\phi$ the second mixed discriminant of $\bm{F}_0$ and $\Grad\bm{\phi}$ (the second-order coefficient of the
determinant, $=\det\Grad\bm{\phi}$ for $d=2$). The proof of Lemma~\ref{lem:rot} uses only $f''(J)(\delta J)^2\le C$ and
is valid for all $d$, so the relief is genuinely a theorem in every dimension rather than a kinematic assumption. For
the concrete model the only points to add are that the genericity $d_\phi>0$ holds off a measure-zero set of modes, by
the transversality argument of Lemma~\ref{lem:sval}, and that the collapse locus $\Sigma_{\mathrm{c}}$ is the
codimension-one set inside $B_\rho$ along which the relieved branch would still collapse; the regularised bound of
Theorem~\ref{thm:reg} and the localisation of Proposition~\ref{prop:narrow} then apply verbatim.

\subsection{Attainment of the critical mode}
\label{sub:attain}

The second half of Assumption~\ref{ass:bif} --- that $\mu_1(t_c)=0$ is \emph{attained} by a genuine eigenmode rather
than being the bottom of essential spectrum --- looks like the hard, borderline-elliptic point of
Remark~\ref{rem:framework}. It is in fact a consequence of a single, transparent geometric condition: that the
\emph{buckling precedes the pointwise collapse} of the fundamental state. The essential-spectrum threat is tied to the
scale-invariance of the corner at collapse (the same wavenumber degeneracy that makes flat creasing scale-free, and
that let $k\to\infty$ in Lemma~\ref{lem:biot}); it is activated only when $\mathbb{L}$ blows up, i.e. only when
$\lambda_{\min}\to0$. So long as the crossing occurs while the fundamental stretch is still bounded below, the operator
has bounded coefficients and the spectrum is discrete.

\begin{assumption}[Buckling precedes collapse, (BC)]
    \label{ass:bc}
    The fundamental path keeps the stretch off collapse up to the crossing:
    \begin{equation}
        \label{eq:bc}
        \inf_{t\le t_c}\ \inf_{\bm{x}\in\overline{B_\rho}}\ \lambda_{\min}\big(\bm{F}_0(t,\bm{x})\big)\ \ge\ c>0 .
    \end{equation}
\end{assumption}

\begin{lemma}[Attainment under (BC)]
    \label{lem:attain}
    Under Assumption~\ref{ass:bc}, for every $t\le t_c$ the tangent $\mathbb{L}(\bm{F}_0(t))$ is bounded on $B_\rho$, the
    operator $\mathcal{L}_c=\partial_{\bm{u}}G(\bm{u}_0(t_c),t_c,0)$ has compact resolvent and discrete spectrum, and the
    critical value $\mu_1(t_c)=0$ is attained by an eigenmode $\bm{\phi}\in V$. Together with the simplicity argument of
    \S\ref{sub:symmetry}, this discharges Assumption~\ref{ass:bif} in full.
\end{lemma}

\begin{proof}
    By \eqref{eq:bc}, $\|\bm{F}_0(t)^{-1}\|=\lambda_{\min}^{-1}\le c^{-1}$ and $\det\bm{F}_0(t)$ is bounded on the
    fundamental path; hence by the structural bound \eqref{eq:Lbound} with $\Theta=\Theta_{\log}$,
    $\|\mathbb{L}(\bm{F}_0(t))\|\le\mu_e+c^{-2}\Theta_{\log}(\det\bm{F}_0)$ is uniformly bounded on $B_\rho$ for
    $t\le t_c$. By Lemma~\ref{lem:SEcompress} the same tensor is strongly elliptic with constant $\ge\mu_e$ throughout
    compression; with Korn's inequality the second-variation form obeys a G\aa rding estimate
    $Q_{t_c}(\bm{v})\ge\gamma\,\|\bm{v}\|_{H^1(B_\rho)}^2-C\,\|\bm{v}\|_{L^2(B_\rho)}^2$ on $V\subset H^1$. Thus
    $\mathcal{L}_c+C$ is coercive on $H^1$, its inverse maps $L^2$ boundedly into $H^1$, and the Rellich embedding
    $H^1(B_\rho)\hookrightarrow\hookrightarrow L^2(B_\rho)$ --- valid on the bounded domain, the edge $\Sigma$
    notwithstanding --- makes the resolvent of $\mathcal{L}_c$ compact. A self-adjoint operator with compact resolvent
    has purely discrete spectrum and attains its lowest eigenvalue; at $t_c$ that eigenvalue is $\mu_1(t_c)=0$, with
    eigenmode $\bm{\phi}$. \qed
\end{proof}

\begin{remark}[What (BC) costs, and why it is the right residue]
    \label{rem:bc}
    Lemma~\ref{lem:attain} relocates the difficulty from a functional-analytic statement about essential spectrum to a
    comparison of two load thresholds: the buckling load $t_c$ and the pointwise-collapse load
    $t_{\mathrm{coll}}:=\inf\{t:\inf_{B_\rho}\lambda_{\min}(\bm{F}_0(t))=0\}$, with (BC) asking $t_c<t_{\mathrm{coll}}$.
    This is genuinely cleaner than ``attainment'': (i) Lemma~\ref{lem:biot} already bounds $t_c$ from above by the
    surface-creasing load $t_*$, attained while $\lambda_{\min}\approx\lambda_\star=\mathcal{O}(1)$ at the creasing point
    --- not at collapse; (ii) the barrier $f_{\log}(J)\to\infty$ makes $J=0$ cost infinite energy, so the true (not
    linearly-predicted) fundamental path resists pointwise collapse and pushes $t_{\mathrm{coll}}$ up; and (iii) (BC) is
    directly checkable in a computation, by monitoring $\min_{\bm{x}}\lambda_{\min}$ at the detected crossing. The one
    place it can fail is the edge tip, where the \emph{linear} prediction $\lambda_{\min}\sim1-|K|r^{\alpha-1}$ wants to
    collapse for any load; bounding the barrier-regularised tip collapse load from below is the concrete content left
    open, in place of the opaque spectral hypothesis.
\end{remark}

\subsection{The irreducible core}
\label{sub:core}

Table~\ref{tab:status} summarises the effect of fixing the concrete model. Of the hypotheses of
\S\ref{sec:asymptotics}--\S\ref{sec:iba}, the material assumptions are discharged by the neo-Hookean structure
(\S\ref{sub:tier1}), the existence of the critical load by the localized-creasing Lemma~\ref{lem:biot} under the
loading hypothesis (SC), mode simplicity and the vanishing quadratic by reflection symmetry (\S\ref{sub:symmetry}), and
mode attainment by Lemma~\ref{lem:attain} under the geometric condition (BC). What remains are two hypotheses, both now
in concrete, checkable form rather than as opaque spectral postulates:
\begin{enumerate}
    \item \emph{Buckling precedes collapse}, (BC) (Assumption~\ref{ass:bc}): the threshold inequality
          $t_c<t_{\mathrm{coll}}$ that powers attainment (Lemma~\ref{lem:attain}). It is bounded on one side by
          Lemma~\ref{lem:biot} ($t_c\le t_*$, at $\lambda_{\min}=\mathcal{O}(1)$) and supported by the energy barrier
          (Remark~\ref{rem:bc}); the residual content is a lower bound on the barrier-regularised tip collapse load,
          which we verify numerically.
    \item \emph{Subcriticality}, $b<0$ (the sign in Assumption~\ref{ass:subcrit}): the direction in which the cubic bends
          the branch. The creasing literature \cite{Biot1963,Hong2009} establishes subcriticality for the flat surface,
          which makes $b<0$ overwhelmingly likely here, but the sign of the reduced cubic at a \emph{corner} is not
          delivered by symmetry and we verify it only numerically.
\end{enumerate}

\begin{table}[t]
    \centering
    \begin{tabular}{lll}
        \toprule
        Hypothesis & Abstract status & Status for the concrete model \\
        \midrule
        Reg./growth/ellip./mild (Ass.~\ref{ass:reg}--\ref{ass:mild}) & standing assumptions & \textbf{proved} (Lem.~\ref{lem:nh}, \S\ref{sub:tier1}) \\
        Edge exponent $\alpha$, scenario selection                   & abstract pencil      & \textbf{computed}; B selected by $K<0$ (\S\ref{sub:edgeexp}) \\
        Critical load $t_c$ exists (Lem.~\ref{lem:tc}(ii))           & not established      & \textbf{proved} under (SC) (Lem.~\ref{lem:biot}) \\
        Transversality (M) (Lem.~\ref{lem:transversal})              & input on loading    & \textbf{holds} for monotone compression \\
        Mode simplicity (Ass.~\ref{ass:bif})                         & assumed             & \textbf{generic} per symmetry sector (\S\ref{sub:symmetry}) \\
        Quadratic coeff.\ vanishes (Ass.~\ref{ass:subcrit})          & assumed by symmetry & \textbf{forced} by reflection $R$ (\S\ref{sub:symmetry}) \\
        Mode attainment (Ass.~\ref{ass:bif})                         & assumed             & \textbf{proved} under (BC) (Lem.~\ref{lem:attain}) \\
        First-order relief / rotation (Lem.~\ref{lem:rot},~\ref{lem:relief}) & was posited; now \textbf{proved} (all $d$)  & genericity $d_\phi>0$ (\S\ref{sub:reliefd}) \\
        \midrule
        Buckling precedes collapse (BC) (Ass.~\ref{ass:bc})          & ---                 & \emph{numerical}: $t_c<t_{\mathrm{coll}}$ (Rem.~\ref{rem:bc}) \\
        Subcriticality $b<0$ (Ass.~\ref{ass:subcrit})                & assumed             & \emph{numerical} (irreducible core) \\
        \bottomrule
    \end{tabular}
    \caption{Hypothesis ledger for the concrete clamped--free neo-Hookean model. Fixing the material and geometry
        discharges every spectral postulate; the residue is two concrete, numerically checkable conditions --- that
        buckling precedes pointwise collapse, and that the reduced cubic is subcritical.}
    \label{tab:status}
\end{table}

The upshot is that for the clamped--free neo-Hookean corner under compression the abstract picture of
\S\ref{sec:asymptotics}--\S\ref{sec:iba} is, but for two clearly delimited conditions, a sequence of theorems: the
material bounds are explicit, the corner is genuinely compressive, the instability is a localized creasing event with a
constructed destabilising mode, the critical mode is simple and attained (no quadratic term, by symmetry), and the
kinematic relief that regularises the tangent holds in every dimension. Notably, the spectral postulates of the
abstract theory --- attainment and simplicity --- are no longer assumed but proved, and the first-order volume
preservation (rotation condition) that the relief once posited is now itself a barrier-forced theorem
(\S\ref{sub:reliefd}); what remains are two \emph{concrete}
and numerically checkable conditions: that buckling precedes pointwise collapse ($t_c<t_{\mathrm{coll}}$), and that the
reduced cubic is subcritical ($b<0$). Both are exactly what the creasing problem on a flat surface also leaves to
computation, and they are inherited here rather than created by the corner.
