%!TEX root = ../main.tex 
\section{Introduction}
\label{sec:intro}
\input{splitted/introduction.tex}

\section{Problem formulation}
\label{sec:formulation}

\section{Asymptotic Behavior of the Neo-Hookean Operator at a Mixed Corner}

\subsection{Problem Setup and Linearized Kinematics}

Let the reference domain $\Omega \subset \mathbb{R}^2$ feature a right-angle corner at the origin $(0,0)$ described by
polar coordinates $(r, \theta)$ for $r \in [0, R]$ and $\theta \in [0, \pi/2]$.
\begin{itemize}
    \item \textbf{Dirichlet Boundary ($\Gamma_D$):} $\theta = 0$, where deformation is prescribed: $y(r, 0) = g(r)$.
    \item \textbf{Neumann Boundary ($\Gamma_N$):} $\theta = \pi/2$, which is traction-free: $P N = 0$.
\end{itemize}

Let $u(x)$ be the displacement, and $F = I + \nabla u$ the deformation gradient. From classical Kondratiev theory for
linear elasticity, the leading-order singular displacement field at this mixed corner behaves as:
\begin{equation}
    u(r, \theta) \sim K r^{\alpha} \Phi(\theta)
\end{equation}
where $K$ is the generalized stress intensity factor (dependent on far-field loading), $\Phi(\theta)$ is a smooth angular
function, and $\alpha \in (0,1)$ is the singularity exponent (typically $\alpha \approx 0.68$ for incompressible
materials).

Consequently, the deformation gradient scales as:
\begin{equation}
    F = I + \mathcal{O}(K r^{\alpha-1})
\end{equation}
As $r \to 0$, $\|F\| \to \infty$. The nature of this singularity---and the resulting behavior of the nonlinear tangent
modulus $L = \frac{\partial^2 \Psi}{\partial F \partial F}$---depends entirely on the sign of $K$ (the loading
direction).

We define a standard compressible neo-Hookean energy density:
\begin{equation}
    \Psi(F) = \frac{\mu}{2} \left( \operatorname{tr}(F^T F) - 2 \right) + f(J)
\end{equation}
where $J = \det(F)$ and $f(J)$ is a strictly convex volumetric penalty function satisfying $f(1)=0$, $f'(1)=-\mu$, and
$f(J) \to \infty$ as $J \to 0$.

The fourth-order tangent modulus $L$ is exactly:
\begin{equation}
    L_{iJkL} = \mu \delta_{ik} \delta_{JL} + \mathcal{B}_{iJkL}(F^{-1}, J)
\end{equation}
where $\mathcal{B}$ contains all nonlinear geometric stiffness terms, bounded by $\| \mathcal{B} \| \leq C(J) \|F^{-1}\|^2$.

\subsection{Scenario A: The Tensile (Non-Compressive) Singularity}

Assume the far-field loading pulls the material away from the corner ($K > 0$ such that the material undergoes radial
tension).

\paragraph{Kinematic consequence.}
The maximum principal stretch $\lambda_{\max}$ aligns roughly radially and blows up as $r^{\alpha-1}$. However, because
the material is pulled outward, the domain locally expands or preserves volume (by drawing material in from the Neumann
boundary). Therefore, the determinant $J$ remains bounded strictly away from zero ($J \geq J_{\min} > 0$), and the
transverse stretch $\lambda_{\min}$ remains finite and non-zero.

\paragraph{Operator behavior.}
Because $\lambda_{\min} > 0$, the inverse deformation gradient is bounded: $\|F^{-1}\| = \lambda_{\min}^{-1} \leq M$.
Looking at the tangent modulus $L$:
\begin{equation}
    \| L(x) \| \leq \mu + C(J) \|F^{-1}\|^2 < \infty \quad \text{as } r \to 0
\end{equation}

\paragraph{Conclusion for Scenario A.}
Although there is a severe \emph{stress singularity} (the First Piola-Kirchhoff stress $P \sim \mu F \to \infty$ as $r
\to 0$), \textbf{there is no singularity in the tangent operator.}
\begin{itemize}
    \item $L$ remains strongly elliptic (the Legendre--Hadamard condition $L_{iJkL}m_i M_J m_k M_L \geq c > 0$ holds).
    \item The standard weak form of the linearized Newton step $\int_\Omega L : \nabla \delta u : \nabla \Delta u \, d\Omega$
          remains uniformly coercive.
    \item The nonlinear neo-Hookean problem behaves exactly parallel to the linear problem. The singularity is safely handled by
          standard weighted Sobolev spaces ($V_\beta^{1,2}$), and no structural instability occurs.
\end{itemize}

\subsection{Scenario B: The Compressive Singularity (The Pathological Case)}

Now, assume the far-field loading pushes the material \emph{into} the corner ($K < 0$, radial compression).

\paragraph{Kinematic consequence.}
The naive linear prediction suggests $\nabla u$ has a negative dominant eigenvalue scaling as $-|K| r^{\alpha-1}$.
Because $F = I + \nabla u$, as we approach the corner ($r \to 0$) or as we increase the pseudo-time load factor $t$,
there exists a critical threshold where the local contraction completely annihilates the material volume:
\begin{equation}
    \det(F) \to 0 \implies J \to 0
\end{equation}
When $J \to 0$, the minimum principal stretch $\lambda_{\min} \to 0$.

\paragraph{Operator blow-up.}
Because $\|F^{-1}\| = \lambda_{\min}^{-1} \to \infty$, the nonlinear operator $\mathcal{B}$ dominates. The tangent
modulus scales asymptotically as:
\begin{equation}
    \| L(x) \| \sim \mathcal{O}(J^{-2}) \sim \mathcal{O}(\|F^{-1}\|^2) \to \infty
\end{equation}

\paragraph{Loss of strong ellipticity.}
Before $J$ even reaches $0$, the extreme compression causes the acoustic tensor $Q_{ik}(N) = L_{iJkL} N_J N_L$ to lose
positive-definiteness. Let $N$ be the normal vector aligned with the direction of maximum compression. The acoustic
tensor associated with this direction will develop a zero, and then negative, eigenvalue:
\begin{equation}
    \min_{m, N} \left( L_{iJkL} m_i N_J m_k N_L \right) \leq 0
\end{equation}
The PDE locally ceases to be elliptic and becomes hyperbolic.

\paragraph{Conclusion for Scenario B.}
The naive assumption that the deformation smoothly follows the fundamental thermodynamic path into the corner leads to
a complete mathematical breakdown. The tangent modulus $L$ becomes infinitely singular ($\|L\| \to \infty$), and the
local operator loses coercivity, meaning standard Newton--Raphson solvers will inevitably fail, and a weak solution for
the linearized step ceases to exist in the standard functional spaces.

This unphysical infinite accumulation of energy ($f(J) \to \infty$) and operator blow-up implies that the assumption of
a smooth deformation path is flawed. In reality, the loss of ellipticity dictates a local geometric bifurcation. To
capture this analytically, we must introduce an imperfect perturbation (noise) to regularize the bifurcation and bound
the singularity.

\section{Imperfect Bifurcation Analysis and Asymptotic Bounds}

\subsection{The Perturbed Weak Form}

We introduce a pseudo-time load parameter $t \in [0, 1]$ which monotonically scales the compressive Dirichlet boundary
conditions. To prevent the unphysical perfect fundamental path ($J \to 0$), we introduce a small, fixed volumetric
perturbation (noise) $\epsilon f(x)$, where $\|f\|_{L^2} = 1$ and $\epsilon \ll 1$.

The nonlinear equilibrium equation in weak form is $G(u, t, \epsilon) = 0$, defined as:
\begin{equation}
    \langle G(u, t, \epsilon), v \rangle = \int_{\Omega} P(F) : \nabla v \, d\Omega - \epsilon \int_{\Omega} f \cdot v \, d\Omega = 0 \quad \forall v \in V
\end{equation}
where $P(F) = \frac{\partial \Psi}{\partial F}$ is the First Piola-Kirchhoff stress, and $V$ is the appropriate space
of kinematically admissible test functions.

\subsection{The Critical Point (Perfect System, $\epsilon = 0$)}

Let $u_0(t)$ be the fundamental path of pure compression (the unphysical path where $J \to 0$ as $t \to 1$). At some
critical load $t_c < 1$, the tangent modulus $L(F_0)$ evaluated on the fundamental path loses positive definiteness.
The linearized operator $\mathcal{L}_c := \partial_u G(u_0(t_c), t_c, 0)$ develops a zero eigenvalue.

Let $\phi \in V$ be the normalized critical eigenmode ($\|\phi\|_V = 1$) associated with this instability (representing
a localized rotation/buckling near the corner). It satisfies:
\begin{equation}
    \int_{\Omega} \nabla \phi : L_c : \nabla v \, d\Omega = 0 \quad \forall v \in V
\end{equation}

\subsection{Lyapunov--Schmidt Reduction (The Normal Form)}

To analyze the perturbed system ($\epsilon > 0$) near $t_c$, we decompose the displacement field into the fundamental
path, the buckling amplitude $w(t, \epsilon)$ along the eigenmode $\phi$, and a higher-order orthogonal remainder $v$:
\begin{equation}
    u(t, \epsilon) = u_0(t) + w \phi + v
\end{equation}
By projecting the weak form onto the eigenmode $\phi$ and applying a standard Taylor expansion of the energy functional
up to the fourth order in $w$, the infinite-dimensional PDE reduces to a scalar algebraic equation for the amplitude
$w$ (the imperfect bifurcation equation):
\begin{equation}
    a (t_c - t) w + b w^3 = \epsilon \eta
\end{equation}
where:
\begin{itemize}
    \item $a = \frac{1}{2} \frac{d}{dt} \langle \phi, \partial^2_u G(u_0(t_c)) \phi \rangle$ is the eigenvalue crossing velocity.
    \item $b = \frac{1}{6} \langle \phi, \partial^3_u G(u_0(t_c)) [\phi, \phi, \phi] \rangle$ governs the post-buckling stiffness (assumed $b > 0$ for a stable supercritical bifurcation).
    \item $\eta = \int_{\Omega} f \cdot \phi \, d\Omega$ is the projection of the noise onto the buckling mode.
\end{itemize}

\subsection{Asymptotic Estimate of the Bifurcation Amplitude}

We are interested in the maximum deformation amplitude, which occurs at or near the critical time $t = t_c$. Evaluated
exactly at $t_c$, the linear term vanishes, leaving:
\begin{equation}
    b w^3 \approx \epsilon \eta
\end{equation}
Thus, the amplitude of the structural instability scales asymptotically with the perturbation:
\begin{equation}
    w(\epsilon) \sim \left( \frac{\eta}{b} \right)^{1/3} \epsilon^{1/3} \quad \text{as } \epsilon \to 0
\end{equation}

\begin{remark}
    Even if the material softening dictates an asymmetric/transcritical bifurcation yielding $w^2 \sim \epsilon$, the
    logic below remains identical with a modified exponent. We proceed with the standard pitchfork $\epsilon^{1/3}$
    scaling.
\end{remark}

\subsection{Kinematic Relief Mechanism: Bounding $J$ and $\|F^{-1}\|$}

The core physical mechanism is that the buckling mode $\phi$ introduces \emph{rotation and shear}, which geometrically
relieves the pure volumetric compression.

At the corner, the total deformation gradient is $F = F_0(t_c) + w \nabla \phi + \mathcal{O}(w^2)$.
\begin{itemize}
    \item $F_0(t_c)$ is a purely compressive state with a minimum principal stretch $\lambda_{c}$, which is small but strictly non-zero ($t_c$ occurs \emph{before} $J \to 0$).
    \item The buckling gradient $\nabla \phi$ represents a symmetry-breaking rotation.
\end{itemize}

Because the instability trades pure compression for bending/rotation, the volumetric determinant $J = \det(F)$ becomes
bounded away from zero by the amplitude of the buckling mode. To leading order, rotations modify the stretch
quadratically. Therefore, the minimum volume ratio is bounded below by:
\begin{equation}
    J_{\min}(\epsilon) \geq C_1 \lambda_c + C_2 w^2
\end{equation}
where $C_1, C_2 > 0$ are geometric constants. As $\epsilon \to 0$ (and assuming $\lambda_c$ approaches some
infinitesimal limit near the theoretical singularity), the dominant bound is provided by the buckling amplitude:
\begin{equation}
    J_{\min}(\epsilon) \sim \mathcal{O}(w^2) \sim \mathcal{O}(\epsilon^{2/3})
\end{equation}

Since $J = \det(F) = \lambda_1 \lambda_2$ (in 2D), and the transverse stretch is largely unaffected or bounded, the
minimum principal stretch scales as $\lambda_{\min} \sim \mathcal{O}(\epsilon^{2/3})$.

Consequently, the norm of the inverse deformation gradient is strictly bounded by the noise:
\begin{equation}
    \| F^{-1} \| = \frac{1}{\lambda_{\min}} \sim \mathcal{O}(\epsilon^{-2/3})
\end{equation}

\subsection{Final Asymptotic Bound on the Tangent Modulus $L$}

Recall from the previous section that the norm of the fourth-order neo-Hookean tangent modulus $L$ is bounded by the
inverse deformation gradient:
\begin{equation}
    \| L(F) \| \leq \mu + \mathcal{K}(J) \|F^{-1}\|^2
\end{equation}
Assuming the volumetric penalty $f(J)$ is chosen such that $\mathcal{K}(J)$ remains bounded or scales no worse than
$J^{-1}$ near $J=0$, the dominant singularity is driven by $\|F^{-1}\|^2$.

Substituting the kinematic bound derived from the imperfect bifurcation analysis:
\begin{equation}
    \max_{x \in \Omega} \| L(x, \epsilon) \| \leq C \| F^{-1} \|^2 \sim \mathcal{O} \left( (\epsilon^{-2/3})^2 \right) = \mathcal{O}(\epsilon^{-4/3})
\end{equation}

\section{Conclusions}
\label{sec:conclusions}

